---
title: "AfreenSiddiqui_Assignment4"
output: html_document
---
##1. FiveThirtyEight Data (30 points): Navigate on GitHub to https://github.com/rudeboybert/fivethirtyeight and read README.md. It includes everything you need.
###a. Install the fivethirtyeight package.
```{r echo=TRUE}
install.packages("fivethirtyeight",repos = "http://cran.us.r-project.org")

```

###b. In the listing of Data sets in package ‘fivethirtyeight,’ assign the eighteenth data set to an object ‘df.’
```{r}
library(fivethirtyeight)
df <- college_recent_grads 
#df
```

###c.Use a more detailed list of the data sets to write out the URL in a comment to the related news story.
```{r}
#vignette("fivethirtyeight", package = "fivethirtyeight")
#https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/
```

### d.Using R command(s), give the dimensions and column names of this data frame.
```{r}
dimens <- dim(df)
columnname <- names(df)
cat("Dimensions are: ", dimens)
cat("Column names are:")
columnname
```

##2. Data Summary (30 points): Use your newly assigned data frame for Question 2.
###a. Write an R command that gives you the column names of the data frame. Right after that, write one that counts the number of columns but not rows. Hint: The number should match one of your numbers in Question 1d for dimensions.
```{r}
columnname <- names(df)
print("Column names are")
columnname
ncol(df)
```

### b.Generate a count of each unique major_category in the data frame. I recommend using libraries to help. To be clear, this should look like a matrix or data frame containing the major_category and the frequency it occurs in the dataset. Assign it to major_count.

```{r}
library(plyr)
major_count <- count(df, "major_code")
major_count
```

###c. To make things easier to read, put par(las=2) before your plot to make the text perpendicular to the axis. Make a barplot of major_count. Make sure to label the title with something informative (check the vignette if you need), label the x and y axis, and make it any color other than grey. Assign the major_category labels to their respective bar. Flip the barplot horizontally so that bars extend to the right, not upward. All of these options can be done in a single pass of barplot(). Note: It’s okay if it’s wider than the preview pane.

```{r}
par(las=2)
par(mar=c(5,8,4,2))
barplot(major_count$major_code, major_count$freq, main = " College Major Category Distribution", xlab = "MajorCode", ylab = "Frequency", col=c("darkblue","red"), horiz = TRUE, cex.name=0.8)
```


###d.Write the fivethirtyeight data to a csv file. Make sure that it does not have row labels.
```{r}
write.csv(df, file='/Users/afreensiddiqui/myhome/SMU/R/MSDS6306/df.csv', row.names=FALSE)
```

##3. Codebook (30 points):
###a. Start a new repository on GitHub for your SMU MSDS homework. On your local device, make sure there is a directory for Homework at the minimum; you are welcome to add whatever you would like to this repo in addition to your requirements here.
```{r}
## https://github.com/AfreenSiddiqui/MSDSRrepo.git

```

